First Order Alternation

### 2019-02-03 quantifiers/body.tex
ok

Even when assuming the alphabet to be finite, complementation of a
finite-state automaton faces an inherent exponential blowup due to
nondeterminism. However, if we allow universal nondeterminsim, in
addition to the classical existential nondeterminism, complementation
is possible is linear time. The automata having both existential and
universal nondeterminism are called \emph{alternating automata}
\cite{ChandraKozenStockmeyer81}. A finite-alphabet alternating
automaton is described by a set of transition rules $q \arrow{a}{}
\phi$, where $q$ is a state, $a$ is an input symbol and $\phi$ is a
boolean formula, whose propositional variables denote successor
states.

>>>>

Even for finite alphabets, complementation of finite-state automata
faces inherent exponential blowup, due to nondeterminism. However, if
we allow universal nondeterminism, in addition to the classical
existential nondeterminism, complementation is possible is linear
time. The automata having both existential and universal
nondeterminism are called \emph{alternating automata}
\cite{ChandraKozenStockmeyer81}. A finite-alphabet alternating
automaton is described by a set of transition rules $q \arrow{a}{}
\phi$, where $q$ is a state, $a$ is an input symbol and $\phi$ is a
boolean formula, whose propositional variables denote successor
states.
